Assessing the Accessibility of Protein Tunnels using Motion Planning

### 2018-02-23 paper.tex
experiments, added new image

The next studied case was the analysis of Leukotriene A4 hydrolase (PDB ID 4L2L).
The task was to find trajectory for the ligand 4-(4-benzylphenyl)-1,3-thiazol-2-amine, which is a known inhibitor of the protein 4L2L.
We therefore assume that the ligand can reach the active site.
%which was in the protein crystal structure (PDB ID 4L2L). 
%Based on the location of inhibitor inside the protein we assume that the inhibitor is able 
The tCONCOORD tool~\cite{seeliger2007geometry} was used to generate 1000 conformations of the protein 4L2L (without the inhibitor).
The initial pdb structure was minimized by GROMACS 4.0.7~\cite{hess2008gromacs} using the input parameters recommended on the example page for tCONCOORD. 
The protein conformations were generated using default settings for tCONCOORD in the PERT mode. % which only perturbs the starting configuration of atoms instead of complete randomization.
The tunnels towards the active site (defined by residues 134 (Alanine) and 311 (Phenylalanine) for probe 0.9~\AA\ were calculated
using CAVER 3.0.
All 1000 conformations contained at least 5 tunnels, more than 900 conformations contained 9 tunnels.
The ordering of the tunnels can slightly change due to conformational changes, so the traversability
to the active site was computed for the first three tunnels (with average bottlenecks 1.22~\AA, 1.20~\AA and 1.19~\AA).
Due to size of the ligand (which has 33 atoms) and the low bottlenecks of the tunnels, we

@@

\begin{figure}
\centering
\caption{\label{fig::inhibitor}Example of inhibitor in 4L2L ... }
\end{figure}

>>>>

The next studied case was the analysis of Leukotriene A4 hydrolase (PDB ID 4L2L).
The task was to find trajectory for the ligand 4-(4-benzylphenyl)-1,3-thiazol-2-amine, which is a known inhibitor of the protein 4L2L.
We therefore assume that the ligand can reach the active site.
%which was in the protein crystal structure (PDB ID 4L2L). 
%Based on the location of inhibitor inside the protein we assume that the inhibitor is able 
The tCONCOORD tool~\cite{seeliger2007geometry} was used to generate 1000 conformations of the protein 4L2L (without the inhibitor).
The initial pdb structure was minimized by GROMACS 4.0.7~\cite{hess2008gromacs} using the input parameters recommended on the example page for tCONCOORD. 
The protein conformations were generated using default settings for tCONCOORD in the PERT mode. % which only perturbs the starting configuration of atoms instead of complete randomization.
The tunnels towards the active site (defined by residues 134 (Alanine) and 311 (Phenylalanine) for probe 0.9~\AA\ were calculated
using CAVER 3.0.
All 1000 conformations contained at least 5 tunnels, more than 900 conformations contained 9 tunnels.
The detected the tunnels slightly differ due to conformational changes.
Therefore, the traversability towards the active site was computed for the first three tunnels (with average bottlenecks 1.22~\AA, 1.20~\AA and 1.19~\AA with the average lengths 22.3~\AA, 25.3~\AA and 28.4~\AA respectively).
The conformations of the ligand were prepared in the same way as in the previous section.
From the available $|\L|=736$ conformations, 100 were selected using the `S' strategy.

@@

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{fig/4l2l-detail}
\caption{\label{fig::inhibitor}Example of inhibitor in 4L2L ... TOOO some better image }
\end{figure}
